\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 learning.tex

We note that linear regression tools are often able to provide an
$n\times 1$ vector $\vec{\delta}$ of error intervals, where the
$i^{th}$ entry of the form $[{\delta_i}_{\min},{\delta_i}_{\max}]$
indicates the best and worst possible error in computation of the
$i^{th}$ state in $\x'$.

Affine maps are poor approximations for arbitrary non-linear
functions. Hence, we use a collection of affine maps to approximate
the local behaviors (in state-space) of the system $\System$. This
results in a piece wise approximation, as described in the next
section.

>>>>

We note that regression tools are often able to provide an
$n\times 1$ vector $\vec{\delta}$ of error intervals, where the
$i^{th}$ entry of the form $[{\delta_i}_{\min},{\delta_i}_{\max}]$
indicates the best and worst possible error in computation of the
$i^{th}$ state in $\x'$.

The choice of kernels for the relational abstraction involves a
tradeoff between computing precise local models and efficiency of the
analysis of the resulting relational abstraction. Affine kernels are
poor approximations for complex dynamics and will result in large
errors, but they can be very efficiently analyzed in practice.  On the
other hand, analysis of arbitrary non-linear functions is still not
tractable. Hence, we restrict ourselves to affine and quadratic
polynomial kernels.  Moreover, as we use a collection of relations to
approximate the local behaviors (in state-space) of the system
$\System$, we can often do away with simple kernels. This however,
results in a piece wise approximation, as described in the next
section.
